Nanophotonic Computational Design

### 2013-02-19 defense/pres2.tex
Added feedback from first practice.
Got basic outline down for pres2.

Goal: Show you how to design \emph{any} linear nanophotonic device
\smallfig{takeaway}
\pause
\BI Device properties: 
    \BI Full 3D
    \I  Compact
    \I  Efficient
    \I  Multi-mode 
    \I  Multi-functional \EI
\nextpage

@@

\I  Obvious and well-known from a mathematical perspective
    \BI Pre-requisite (200-level) class in optimization curriculum
    \I  Not yet taught (I think) in optics/photonics at Stanford \EI
    \stepwise{\step{
    \BE
    \underbrace{\nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
                -i \omega J }_\text{physics}
    \quad\longrightarrow\quad
    \underbrace{A(z)x = b}_\text{linear algebra}
    \EE
    \begin{align*}
    E &\to x \\
    \epsilon &\to z \\
    \nabla\times\mu_0^{-1}\nabla\times - \omega^2 \epsilon &\to A(z) \\
    -i\omega J &\to b
    \end{align*}
    }
\step{\I  Key: If $A(z)$ is linear in $z$ then $A(z)x=b$ is as well!}
    }

>>>>

\oursection{Introduction}
\smallfig{optical_networks}
\BI  Bring the optical network onto a computer chip
\nextpage

\smallfig{integrated_circuit}
\I  Currently designed by hand, handful of parameters
\I  Design by computer, using the full design parameters
\nextpage

\I  Increasing design complexity requires additional degrees of freedom
\I  Fortunately, we have a virtually unlimited amount
\smallfig{des_complexity}
\I  Include/exclude per pixel gives us $2^{(15^2)} = 2^{225}$ possibilities, 
    uncountable
\nextpage

Goal: Show you how to design \emph{any} linear nanophotonic device
\smallfig{takeaway}
\pause
\I Device properties: 
    \BI Full 3D
    \I  Compact
    \I  Efficient
    \I  Multi-mode 
    \I  Multi-functional \EI
\nextpage

@@

\I  Obvious and well-known from a mathematical perspective
    \BI Pre-requisite (200-level) class in optimization curriculum
    \I  Not yet taught (I think) in optics/photonics at Stanford \EI
    \stepwise{\step{
    \BE
    \underbrace{\nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
                -i \omega J }_\text{physics}
    \quad\longrightarrow\quad
    \underbrace{A(z)x = b}_\text{linear algebra}
    \EE
    }
    \step{
    \begin{align*}
    E &\to x \\
    \epsilon &\to z \\
    \nabla\times\mu_0^{-1}\nabla\times - \omega^2 \epsilon &\to A(z) \\
    -i\omega J &\to b
    \end{align*}
    }
\step{\I  Key: If $A(z)$ is linear in $z$ then $A(z)x=b$ is as well!}
    }

\oursection{Direct design of nanophotonic devices}
\I  Choose $x$ (field) and solve for $z$ (structure)
\smallfig{1d_leastsquares}
\I  Perfect performance!\ldots But unmanufacturable structure
\nextpage

\bigfig{1d_regularized_23}
\I  Regularization on $z$ decreases performance 
\nextpage

\I  Conclusion: 
    \BI Directly solving for $z$ (structure) is easy
    \I  Solving for manufacturable $z$ is hard \EI
% \smallfig{1d_regularized_2}
\I  However, we know that there exist some $x$ (fields) 
    which produce well-behaved $z$ (structure)
    \BI But, cannot ask the user to choose such $x$ \EI
\nextpage

\oursection{Iterative design of nanophotonic devices}
\I  Key lesson: Nanophotonic design involves 
    optimizing \emph{both} $x$ (field) and $z$ (structure)

\I  New algorithm: Iteratively solve for $x$ and $z$
    \begin{align*} 
    \minimize_z & \|A(z)x - b\|^2 + \eta_0\|z - z_0\|^2 \\
    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_0\|^2 
    \end{align*}

\I  Here, $\eta_{0,1}$ are \emph{regularization} parameters
\nextpage

\I  Iterative strategy produces $z$ (structure) that 
    \BI is better behaved
    \I  more accurately produces $x$ \EI
\smallfig{1d_alternate}
\nextpage

\I  We can also put hard limits on $z$
    \begin{align*} 
    \minimize_z & \|A(z)x - b\|^2 \\
    \subto & z_0 \le z \le z_1 \\ \\
    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_0\|^2 
    \end{align*}
\I  $z_0 \le z \le z_1$ constraint better represents manufacturability constraint
    \BI Corresponds to a minimum and maximum allowable permittivity ($\epsilon$) \EI
\nextpage

\smallfig{1d_hardlimit}
\I  Getting close!
\nextpage

\I  higher dimensions
\myfig{2d_circ}{5}
\myfig{25d_circ}{5}
\nextpage

\oursection{Objective-first design of nanophotonic devices}
\I  Next step in our thinking is that for most devices only some parts of the field matter
\I  waveguiding devices
\medfig{ob1_wg}

\oursection{Design of 3D nanophotonic devices}
